Multiscale Understanding the Wettability of Doped Two-Dimensional Materials

### 2017-06-01 writing/paper-Tian-gr-wetting.tex
Minor change and clean up files

% Created 2017-02-22 Wed 21:46
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\date{}
\title{Wettability of Doped Two-Dimensional Materials}
\begin{document}

\newpage{}
\begin{abstract}
  Understanding molecular interactions between liquid and the doped two-dimensional (2D) 
  materials enables new technology opportunities in functional surfaces and ultrathin membranes. 
  Here, we develop the first theoretical framework to model the wettability of the doped two-dimensional 
  (2D) materials as a function of their doping level. Multiscale physical phenomena are considered, 
  including: (i) the change of 2D materials surface energy, 
  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
  and (iii) the electrical double layer (EDL) formed in the liquid phase. 
  \textcolor{cyan}{We propose that the EDL effect dominates the contact angle change }
  and show that upon doping, the decrease of the equilibrium water contact angle on a sheet of defect-free, 
  monolayer 2D material is typically less than 7 degrees. 
  We then study the role of the surface defects and the influence of 2D material choice.
  \textcolor{cyan}{Our analysis show that the defect density plays a crucial role in the water contact angle on the doped
  2D materials, and is responsible for the discrepancy between the recent experimental observations and our proposed 
  theory. Based on the quantum capacitances (QCs) of various 2D materials calculated by density functional theory (DFT),
  we predict that when the the 2D material is doped by electrostatic gating, 
  the contact angle change on 2D semiconductors (e.g. transition metal dichalcogenides (TMDCs)) is more
  sensitive to the gate voltage compared to that on 2D semimetals (e.g. graphene). 
  Selecting a 2D material with a higher QC essentially reduces the gate voltage required to reach the same doping level,
  and ensures a wider operational region in 2D-material-based liquid phase devices.}
  \textcolor{magenta}{
  FINAL CONCLUSIONS PLACE HOLDER.
  }

\end{abstract}
\maketitle

\section{Introduction}
\label{sec:org30908ab}

Two-dimensional (2D) materials, the crystalline films with a thickness
of one atom or one molecule, combine optical transparency and the
quantum-confined properties.
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} [cite some review papers].

\end{minipage}
}
\end{center}
Recent progress in the scalable production of large-area 2D materials
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} cite review papers

\end{minipage}
}
\end{center}
has paved the way for the applications of functional surfaces and
ultrathin membranes.
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} cite review papers

@@

The realization of these technologies essentially requires precise
control over the interactions between liquid and the ultrathin
materials, which motivates fundamental research of their
wettability. An accurate determination of the interfacial tension,
nevertheless, remains highly disputed
\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}. Early
literature on understanding the surface science of 2D materials has
highlighted the effects of the airborne contaminants
\cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014,Kozbial_2015,Chow_2015}
and the underlying substrate
\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
since the length scale for the van der Waals (vdW) interactions is
comparable to the thickness of a monolayer. On the other hand, a
subtle but important fact is that the 2D semimetals (e.g, graphene and
silicene) and 2D semiconductors (e.g., transition metal
dichalcogenides (TMDCs)) possess low density of states (DOSs) around
the intrinsic Fermi level (\(E_{\mathrm{F}}\)), such that the effect of
doping, either induced by the surroundings
\cite{Chen_2013,Varchon_2007,Giovannetti_2008}, or by the electrostatic
gating \cite{Das_2008,Perera_2013}, also comes into play. Very recently,
the doping-induced change in the wettability of graphene has been
observed in the contact-angle experiments
\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016},
and the molecular dynamics (MD) simulations
\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. However,
most reports described the doping-dependent wettability with the basic
Young-Lippmann equation (YLE) \cite{Lippmann_1875}, whereas the
interplay between the polar orientation of water molecules at the
interface \cite{Shen_2006} and the electronic structure of the 2D
materials is often ignored. In order to address the discrepancies
among the literature, a more complete theoretical picture that bridges
the gap between different length scales is clearly required.

>>>>

% Created 2017-06-01 Thu 19:09
% Intended LaTeX compiler: pdflatex
\documentclass[journal=jacsat,manuscript=article,email=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\keywords{Two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, eletrical double layer}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy & Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy & Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\date{}
\title{Multiscale Understanding the Wettability of Doped Two-Dimensional Materials}
\begin{document}

\newpage{}
\begin{abstract}
  Engineering molecular interactions at two-dimensional (2D) materials interfaces enables new technological opportunities 
  in functional surfaces and molecular epitaxy. Quantifying the interplay between the interfacial forces and electric 
  potential of 2D materials represents the crucial first step for understanding their wettability.
  Here we develop the first theoretical framework to model the wettability of the doped 2D 
  materials by properly bridging the multiscale physical phenomena at the 2D interfaces,
  including: (i) the change of 2D materials surface energy (atomistic scale), 
  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
  (molecular scale), and (iii) the electrical double layer (EDL) formed in the liquid phase (macroscopic scale). 
  The latter two effects are found to be the major mechanisms responsible for the contact angle change upon doping.
  When the doping level is electrostatically tuned, we demonstrate that 2D materials with high quantum capacitances 
  (e.g., transition metal dichalcogenides, TMDCs) possess a wider range of tunability in the interfacial tension. 
  Furthermore, practical considerations such as defect and airborne contamination are also quantitatively discussed. 
  Our analysis implies that the doping level can be another variable to modulate the wettability at the interface of 2D materials,
  as well as the molecular packing behavior on a 2D material-coated surface, 
  essentially faciliating the interfacial engineering of 2D materials.
\end{abstract}
# \maketitle

\newpage{}

\section{Introduction}
\label{sec:org435dbee}

Two-dimensional (2D) materials, the crystalline films with a thickness
of one atom or one molecule, combine optical transparency and the
quantum-confined properties
\cite{Novoselov_2005,Mas_Ballest__2011,Novoselov_2016}.  Recent progress in the scalable production of large-area 2D
materials \cite{Boott_2015,Li_2016} has paved the way for the
applications of functional surfaces and ultrathin membranes
\cite{Prasai_2012,Feng_2016,Rafiee_2010,Yin_2014,Surwade_2015,Hern_ndez_2013}.
The concept of van der Waals (vdW) epitaxy has been further extended
to grow molecular heterostructures on 2D material-coated surfaces for
a variety of applications
\cite{Shi_2012_epitaxy_graphene,Kim_2017_remote_epitaxy,Novoselov_2016}. The
realization of these technologies essentially requires precise control
over the molecular interactions at 2D material interfaces, which
motivates fundamental research of their interfacial properties, in
particular the wettability.  An accurate determination of the
interfacial tension, nevertheless, remains highly disputed
\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}. Early
literature on understanding the surface science of 2D materials has
highlighted the effects of the airborne contaminants
\cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014,Kozbial_2015,Chow_2015}
and the underlying substrate
\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
since the length scale for the van der Waals (vdW) radius is
comparable to the thickness of a monolayer. On the other hand, a
subtle but important fact is that the 2D semimetals (e.g, graphene and
silicene) and 2D semiconductors (e.g., transition metal
dichalcogenides (TMDCs)) possess low density of states (DOSs) around
the intrinsic Fermi level (\(E_{\mathrm{F}}\)), such that the effect of
doping, either induced by the surroundings
\cite{Chen_2013,Varchon_2007,Giovannetti_2008}, or by the electrostatic
gating \cite{Das_2008,Perera_2013}, also comes into play. Recent advance
in the \textit{ab initio} calculations and scanning tunneling
microscopy (STM) studies on the adsorbed molecules on graphene
\cite{Muruganathan_2015,Huttmann_2015} has provided some clues to the
doping-dependent vdW interactions. Subsequently, the doping-induced
change in the wettability of graphene has been observed in the
contact-angle experiments
\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016},
and the molecular dynamics (MD) simulations
\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. In
this respect, however, most reports described the doping-dependent
wettability with the basic Young-Lippmann equation (YLE)
\cite{Lippmann_1875}, whereas the interplay between the orientation of
liquid molecules at the interface \cite{Shen_2006} and the electronic
structure of the 2D materials is often ignored. In order to address
the discrepancies among the literature, a general and complete
theoretical picture that bridges the gap between different length
scales, is clearly required.

In this report, we propose the first theoretical framework to model
the change of interfacial tension between liquid and a sheet of
monolayer 2D material. Multiscale physical phenomena are
considered. At the atomistic scale, we formulate the dependence of
surface energy of a 2D material on the doping density using the
quantum capacitance (QC) calculated by the density functional theory
(DFT). Next, the surface-charge-induced reorientation of liquid
molecules adjacent to the interface is associated with an N-body
system, which is resolved by molecular dynamics (MD) simulations,
allowing quantification of the interfacial tension in the absence of
electrolytes in liquid. The effect of the electrical double layer
(EDL) induced by the electrostatic interactions between the 2D
material surface charges and the ionic species in liquid, is then
addressed at the continuum level. Practical considerations, such as
the defect density and the surface contamination are also taken into
account to provide a comprehensive understanding of the
phenomena. Finally, we examine and validate our theory by comparing
with the contact angle changes reported in the electrowetting and the
substrate-induced doping experiments.

\section{Results and Discussions}
\label{sec:org66b0b42}

\subsection{Surface Energy of Doped 2D Materials}
\label{sec:org87cc68c}

Consider a liquid (\emph{L}) droplet sitting on a flat, monolayer 2D
material (\emph{2D}) supported by a solid substrate, following the Young’s
equation, the change of the equilibrium contact angle \(\theta\) upon
doping, is given by
\begin{equation}
\label{eqn-def-Young-Delta-theta}
\gamma_{\mathrm{L}} \Delta \cos\theta = \Delta \gamma_{\mathrm{2D}}
                                 - \Delta \gamma_{\mathrm{2D-L}}
\end{equation}
where \(\gamma_{\mathrm{L}}\) and \(\gamma_{\mathrm{2D}}\) are the surface
tensions of liquid and the 2D material considered,
respectively, \(\gamma_{\mathrm{2D-L}}\) is the interfacial tension between the
liquid and the contacting 2D material. We define \(\Delta \gamma =
\gamma - \gamma_{0}\) for all the surface (interfacial) tensions considered and
\(\Delta \cos \theta = \cos \theta - \cos \theta_{0}\), where the
subscript 0 corresponds to that in the case of intrinsic 2D material,
with the doping density per unit area, \(\sigma_{\mathrm{2D}} = 0\). In
the theoretical analysis presented here, we aim to model \(\Delta \cos
\theta\) as a function of \(\sigma_{\mathrm{2D}}\). Note that under the
assumptions that (i) the change of \(E_{\mathrm{F}}\) in the doped 2D
materials does not result in the interfacial electron transfer,
namely, the electrochemical reactions, (ii) the doping effect does not
change the surface energy of the underlying substrate, and (iii) the
vdW and electrostatic interactions are perfectly additive and
pairwise, one can decouple the effect of the underlying
substrate. Therefore the debate of the “wetting transparency”
\cite{rafiee_wetting_2012,shih_wetting_2013}, does not affect our analysis.

First, we model the dependence of \(\gamma_{\mathrm{2D}}\) on the doping
level. Consider a closed system with constant pressure and volume
containing a sheet of free-standing 2D material, following the Euler
homogeneous function theorem of thermodynamics, the total internal
energy of the system \(U\), is given by \(U = TS + \mu_{\mathrm{2D}} N +
\gamma_{\mathrm{2D}} A + \psi_{\mathrm{2D}} q\)
\cite{bard_electrochemical_1980}, where \(T\) is the temperature, \(S\) is
the entropy, \(\mu_{\mathrm{2D}}\) is the chemical potential of the 2D
material per unit lattice, \(N\) is the number of unit lattices, \(A\) is
the area of the 2D material, and \(\psi_{\mathrm{2D}}\) and \(q\) are the
electric potential and total charge in the 2D material,
respectively. At constant \(T\), combining with the first law of
thermodynamics and the differential form of \(U\), it follows:
\begin{equation}
\label{eqn-dgamma-dpsi}
\mathrm{d} \gamma_{\mathrm{2D}} = -\frac{q}{A} \mathrm{d} \psi_{\mathrm{2D}}
                                = -\sigma_{\mathrm{2D}} \mathrm{d} \psi_{\mathrm{2D}}
\end{equation}
relating the surface tension change of a free-standing 2D material as
a function of its doping density \(\sigma_{\mathrm{2D}}\). After bringing an amount of charge
\(q\) from infinity to a charge-neutral 2D material in the
aforementioned system, the surface energy change is therefore given
by:
\begin{equation}
\label{eqn-delta-gamma-sigma-free-2D}
\Delta \gamma_{\mathrm{2D}} = - \int_{0}^{\psi_{\mathrm{2D}}} \sigma_{\mathrm{2D}} \mathrm{d}\psi'
                            = - \int_{0}^{\sigma_{\mathrm{2D}}} \sigma' \left( \frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d} \sigma'
\end{equation}
where \(C_{\mathrm{2D}} = g(E_{\mathrm{F}}) e^{2}\) is the quantum
capacitance of the 2D material \cite{davies_two-dimensional_1997,Das_Sarma_2011},
\(g(E_{\mathrm{F}})\) is the DOS as a function of \(E_{\mathrm{F}}\),
\(\psi_{\mathrm{2D}} = -(E_{\mathrm{F}} - E_{\mathrm{F,0}})/e\) and
\(E_{\mathrm{F,0}}\) corresponds to the Fermi level of the 2D material
at the charge neutral point (CNP). Accordingly, eq
\ref{eqn-delta-gamma-sigma-free-2D} provides a simple relation which
depicts the surface tension change of a 2D material at the
quantum-mechanical level. We have calculated the DOSs as a function of
\(E_{\mathrm{F}}\) for a variety of 2D materials using the density
functional theory \cite{tian_multiscale_2016}. Note that we take into
account a fractional component of the exact exchange from the
Hartree-Fock (HF) theory hybridized with the DFT exchange-correlation
functional at the level of the HSE06 hybrid functional. Therefore, any
limitation of the exchange and correlation functional utilized in the
chemical description of the energy levels can be improved. The
following 2D materials are considered: TMDC monolayers (MX\(_{\text{2}}\), M =
Mo, W and X = S, Se, Te), silicene, germanene, phosphorene (monolayer
black phosphorus), and graphene. The doping density in a 2D material
is calculated by integrating the DOS from its intrinsic Fermi level,
i.e., \(\sigma_{\mathrm{2D}} = \int_{E_{\mathrm{F,0}}}^{E_{\mathrm{F}}}
g(E')e \mathrm{d}E'\) \cite{john_quantum_2004}.

Figure \ref{fig:dgamma-sigma} presents the calculated \(\Delta
\gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for the
2D materials considered here. Clearly, the doping of 2D materials
reduces their surface energy, or based on the classical definition,
the work required to separate two stacked monolayers is lowered. Among
the 2D materials, we find that graphene shows the highest degree of
surface energy decrease, up to -16 mJ\(\cdot \mathrm{m}^{-2}\) , or
\textasciitilde{}20\% reduction of its intrinsic surface tension
\cite{shih_wetting_2013}, at \(\sigma_{\mathrm{2D}}\) = \(\pm
4\times10^{13}\ e\cdot \mathrm{cm}^{-2}\). However, as will be
discussed later, it does not imply a reduced wettability because the
quantum capacitance effect also reduces the interfacial tension,
\(\gamma_{\mathrm{2D-L}}\). A clear trend is that the surface energy
decrease is more significant in the 2D semimetals (e.g. graphene,
silicene, and germanene) than that in the 2D semiconductors
(e.g. TMDCs). This reflects the fact that the effective mass of
carriers in the 2D semiconductors is much higher than that in the 2D
semimetals \cite{davies_two-dimensional_1997}, thereby resulting in
high DOS, as well as a high \(C_{\mathrm{2D}}\) (see eq
\ref{eqn-delta-gamma-sigma-free-2D}). This concept also explains why the
surface energy decrease for silicene and germanene are lower than
that for graphene \cite{Yan_2013}.  To our knowledge, the doping-induced
surface energy change in 2D materials has never been investigated
experimentally, which may be of interest for future study.

\subsection{Reorientation of Liquid Molecules}
\label{sec:org188528c}

Next, we discuss the interactions between 2D materials and liquid. In
a doped 2D material, the delocalized carriers are confined in the 2D
plane. Therefore, following the spirit of the mean-field theory, we
treat it as a continuously, uniformly charged surface. Since these
charges are either generated by interacting with the underlying
substrate, or electrostatically induced by gating, the
electroneutrality still holds before in contact with liquid. The
surface charges result in two consequences that may change
\(\gamma_{\mathrm{2D-L}}\), including (i) the reorientation of adjacent
liquid molecules \cite{ostrowski_tunable_2014} and (ii) the formation of
the electric double layer (EDL) at the liquid-solid interface, known
as the electrowetting effect
\cite{Lippmann_1908,mugele_electrowetting:_2005}. Under the assumption
that the vdW and electrostatic (Coulombic) interactions are additive,
which compose the interfacial tension, we propose that the
interfacial tension change is given by:

\begin{equation}
\label{eqn-delta-gamma-decompose}
\Delta \gamma_{\mathrm{2D-L}} = \Delta \gamma_{\mathrm{2D-L}}^{\mathrm{Orien}}
                              + \Delta \gamma_{\mathrm{2D-L}}^{\mathrm{EDL}}
\end{equation}
where \(\Delta \gamma_{\mathrm{2D-L}}^{\mathrm{Orien}}\) and \(\Delta
\gamma_{\mathrm{2D-L}}^{\mathrm{EDL}}\) correspond to the contributions
from the reorientation and the EDL effects, respectively, as
schematically illustrated in Figure \ref{fig:scheme-method}. We also
assume that \(\Delta \gamma_{\mathrm{2D-L}}^{Orien}\) is independent of
the electrolyte concentration, since the concentration of liquid
molecules is typically orders-of-magnitude higher.

First we discuss the orientation effect. Understanding the
reorientation effect involves positioning and sampling the collective,
time-averaged motion of liquid molecules near the interface, which is
a standard molecular dynamics (MD) problem. Note that even with the
state-of-the-art MD algorithms, it remains challenging to accommodate
the calculations for the EDL, in which the length scale of electric
field can be larger than one micrometer in diluted electrolyte
solutions, e.g., pure water with self-ionized H\(_{\text{3}}\)O\(^{\text{+}}\) and OH\(^{\text{-}}\)
ions. Here we consider the graphene-water interface as a model
system. All MD simulations were carried out using the GROMACS 4.5
software package \cite{Hess_2008}. Monolayer graphene was modeled as an
infinite rigid sheet in the x-y plane. The carbon atoms of graphene
were treated as uncharged Lennard-Jones (LJ) spheres with \(\sigma\) =
0.34 nm and \(\epsilon\) = 0.223 kJ/mol \cite{Cheng_1990}, using the
force-field parameters reported by Tummala and Striolo
\cite{Tummala_2008}. The doping effect is included by assigning an equal
amount of charge \(\sigma_{\mathrm{2D}} / \rho_{\mathrm{G}}\), where
\(\rho_{\mathrm{G}}\) is the surface density of carbon atoms, to each
carbon atom. The \(\sigma_{\mathrm{2D}}\) range considered here
approximately correspond to the partial atomic charge from −0.012 to
0.012 \(e/\mathrm{atom}\). Water molecules were modeled using the SPC/E
model \cite{Berendsen_1987} with bond lengths and angles of water
molecules constrained using the SETTLE algorithm
\cite{Miyamoto_1992}. Lennard-Jones interactions were treated with a
cutoff distance of 1 nm, with those between different atoms calculated
using the standard geometric averaging rule. Long-range electrostatic
interactions were treated using the particle mesh Ewald (PME)
summation method \cite{Darden_1993,Essmann_1995} with a short-range
cutoff distance of 1 nm. The velocity-rescaled Berendsen thermostat
was implemented to maintain a constant system temperature of 298.15 K
\cite{Bussi_2007}. All simulations were carried out under the NVT
ensemble.

In order to precisely determine the interfacial interactions using MD
simulations, instead of the commonly used model that compared the
nanoscale contact angle by placing a nanodroplet onto a sheet of
suspended 2D material
\cite{ostrowski_tunable_2014,daub_electrowetting_2007,ren_interfacial_2015,Taherian_2015},
we simulate the difference of the total potential energy, \(E\), between
two separate systems that contain (i) only water molecules with two
surfaces exposing to vacuum (L), and (ii) the same amount of water
molecules with one surface in contact with graphene (placed at z = 0)
and the other surface exposing to vacuum (GL) (see Figure
\ref{fig:MD-res}(a) and \ref{fig:MD-res}(b)) . Periodic boundary
conditions are used in all three directions of the simulation boxes in
both systems. Additionally, a vacuum layer of 3 nm thick along the
\emph{z}-axis is placed to separate the periodic images of the
graphene-water system. The total energy in both systems can be
formulated as: \(E_{\mathrm{L}} = \mu_{\mathrm{L}}n_{\mathrm{L}} +
2\gamma_{\mathrm{L}}S\) and
\(E_{\mathrm{GL}}=\mu_{\mathrm{L}}n_{\mathrm{L}}+(\gamma_{\mathrm{L}} +
\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}})S\), respectively, where
\(\mu_{\mathrm{L}}\) is the chemical potential per water molecule in the
bulk phase, \(n_{\mathrm{L}}\) is the number of liquid molecules in the
simulation box, and \(S\) is the area of the \emph{xy}-plane.  A simulation
box with a sufficiently large length of 21 nm in the \emph{z}-direction is used,
with a 18-nm thick block of water molecules, to minimize the effect of
the long-range electrostatic interaction between the charged graphene
and the water molecules at the water-vacuum interface, by ensuring
that the time-averaged dipole moment for the water molecules at the
water-vacuum interface is approximately zero (see Supporting Information
Figure S1).  One can show that \(E_{\mathrm{GL}} - E_{\mathrm{L}} =
(\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}} - \gamma_{L})S =
(\Phi + 2 \gamma_{\mathrm{2D}})S\), where \(\Phi\) is the interfacial
energy, which is defined as \(\Phi = \gamma_{\mathrm{2D-L}} -
\gamma_{\mathrm{2D}} - \gamma_{\mathrm{L}}\), and combining with eq
\ref{eqn-def-Young-Delta-theta}, the change of interfacial energy
\(\Delta \Phi\) can be formulated as:
\begin{equation}
\label{eqn-Delta-Phi-Delta-cos}
\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S - 2\Delta \gamma_{\mathrm{2D}} = -\gamma_{\mathrm{L}} (\Delta \cos \theta)^{\mathrm{Orien}}
\end{equation}
where \((\Delta\cos \theta)^{\mathrm{Orien}}\) corresponds to the
contact angle change due to the reorientation effect. Note that in the
current MD simulation setup, the surface tension of the 2D material
remains unchanged (i.e. \(\Delta \gamma_{\mathrm{2D}}=0\)), since the
Fermi level change with
respect to \(\sigma_{\mathrm{2D}}\) (see eq
\ref{eqn-delta-gamma-sigma-free-2D}) is not included in the algorithm. In all simulations we assume a
constant surface tension of water \(\gamma_{\mathrm{L}}=72.8\
\mathrm{mJ}\cdot \mathrm{m}^{-2}\). Accordingly, \(\Delta \Phi\) follows
\(\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S = \Delta
\Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{Coul}}\), where \(\Delta
\Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) correspond to
the change for the vdW and Coulombic interaction potentials,
respectively.

Figure \ref{fig:MD-res}(c) shows the values of \(\Delta \Phi\), and its
contributions from the Lennard-Jones (\(\Delta \Phi_{\mathrm{LJ}}\)) and
Coulombic interactions (\(\Delta \Phi_{\mathrm{Coul}}\)), as functions
of \(\sigma_{\mathrm{2D}}\). We note that the change of adhesion energy
in the doped graphene system is dominated by the Coulombic
interaction. When the doping level of graphene is \(\pm 4 \times
10^{13}\ e\cdot \mathrm{cm}^{-2}\), the Coulombic interaction causes a
decrease in the adhesion energy of -10\textasciitilde{}-15 mJ\(\cdot \mathrm{m}^{-2}\),
while the vdW interaction, on the other hand, causes a slight increase
in the adhesion energy by less than 5 mJ\(\cdot \mathrm{m}^{-2}\). In
other words, concerning the reorientation of water molecules at high
doping levels, the Coulombic interaction favors the decrease of
\(\gamma_{\mathrm{2D-L}}\), and thus the contact angle \(\theta\), while
the vdW interaction slightly increases \(\gamma_{\mathrm{2D-L}}\) and
\(\theta\). We shall note that due to the highly polar nature of water
molecules, the average inter-molecular equilibrium distance in the
absence of external electric field is shorter than the Lennard-Jones
equilibrium distance. Increasing the doping density of the graphene
sheet essentially enhances the electrostatic attractions between
graphene and water molecules and further decreases the inter-molecular
equilibrium distance, as reflected from the red shifts of the first
peaks in Figure \ref{fig:MD-res}(d) for the two charged graphene cases
compared to the charge-neutral case, which eventually leads to a
slight increase in .  The plot of \(\Delta \Phi\) as a function of
\(\sigma_{\mathrm{2D}}\) in Figure \ref{fig:MD-res}(b) shows an apparent
asymmetric shape. This is can be further revealed from the
\emph{z}-dependent local molecular density \(\rho_{\mathrm{L}}\) and charge
density \(\delta_{\mathrm{L}}\) profiles of the water molecules, as
shown in Figure \ref{fig:MD-res}(d) and \ref{fig:MD-res}(c),
respectively. The molecular density of the first water layer adjacent
to graphene increases when graphene is p-doped
(\(\sigma_{\mathrm{2D}}=0.012\ e\cdot \mathrm{cm}^{-2}\), or
equivalently 4.56 \textit{e}/atom) and decreases when graphene is
n-doped (\(\sigma_{\mathrm{2D}}=-0.012\ e\cdot \mathrm{cm}^{-2}\), or
equivalently 4.56 \textit{e}/atom) compared with the case of
charge-neutral graphene, indicating the polarity-dependent adsorption
of water molecules on graphene. Similar trend can also be observed in
the \(\delta_{\mathrm{L}}\) profiles. Interestingly, \(\Delta \Phi\)
exhibits positive Coulombic contribution for slightly n-doped
graphene, when \(\sigma_{\mathrm{2D}} \approx -2\times10^{13}\ e\cdot
\mathrm{cm}^{-2}\), indicating that the reorientation of interfacial
water molecules by small negative charges on graphene helps minimizing
the Coulombic interactions.
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} Explanation of the positive part of \(\Delta \Phi\) when \(\sigma_{\mathrm{2D}} \approx -2\) ?

\end{minipage}
}
\end{center}
Although the MD simulation results show the Coulombic interaction
between the doped graphene and water molecules dominate the
reorientation effect, such conclusion may not be readily applied to
other types of 2D materials. For 2D semimetal systems (silicene and
germanene), the intensity of Coulombic interactions may vary due to
the mismatch among the lattice constants. On the other hand, for the
2D semiconductors such as the TMDCs, in which their
\(\gamma_{\mathrm{2D-L}}\) are already largely determined by the
Coulombic interactions in the intrinsic case
\cite{Govind_Rajan_2016,Chow_2015}. Therefore we anticipate that
case-by-case studies and DFT calculations which deal with the
post-doping charge redistribution, might be required.
\begin{center}
\fbox{
\begin{minipage}[c]{.8\linewidth}
\textbf{\textsf{\textsc{TODO}}} Try find other references?

@@

\subsection{Electrical Double Layer Effect}
\label{sec:org0491aea}

The EDL effect that decreases the interfacial tension has been
extensively studied in the context of the electrowetting phenomena
\cite{Mugele_2005}, in which the interfacial tension is reduced due to
the adsorption of ionic species at the solid-liquid interface. Here we
extend the concept to the 2D material-liquid systems. Consider a
closed system containing an interface formed between liquid and a
sheet of free-standing 2D material, by combining with the Gibbs
adsorption theory \cite{bard_electrochemical_1980}, one can obtain:
\begin{equation}
\label{eq:2}
\mathrm{d} \gamma_{\mathrm{2D-L}}^{\mathrm{EDL}} = -\sigma_{\mathrm{2D}} \mathrm{d} \psi_{\mathrm{2D}}
                                                   -\sum_{\mathrm{i}} \Gamma_{\mathrm{i}} \mathrm{d}\mu_{\mathrm{i}}
\end{equation}
where \(\Gamma_{\mathrm{i}}\) and \(\mu_{\mathrm{i}}\) are the interfacial
excess and the chemical potential of the ionic specie \(i\) at the
interface, respectively. Relative to that in the bulk phase
(\(\psi=0\)), the interfacial chemical potential of a charged solute
\(\mu_{\mathrm{i}}\), is given by
\(\mu_{\mathrm{i}}=z_{\mathrm{i}}e\psi_{\mathrm{2D}}\), where
\(z_{\mathrm{i}}\) is the valency of component \(i\), under the assumption
that the interfacial electric potential is equal to
\(\psi_{\mathrm{2D}}\). As with the approach leading to eq
\ref{eqn-delta-gamma-sigma-free-2D}, it follows:
\begin{equation}
\label{eqn-Delta-gamma-2DL-EDL-full}
\Delta \gamma_{\mathrm{2D-L}}^{\mathrm{EDL}} = 
-\int_{0}^{\sigma_{\mathrm{2D}}} \sigma' \left(\frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d}\sigma'
-\int_{0}^{\sigma_{\mathrm{L}}} \sigma' \left(\frac{1}{C_{\mathrm{EDL}}}\right) \mathrm{d}\sigma'
\end{equation}
where \(\sigma_{\mathrm{L}}\) is the interfacial charge density per unit
area in the liquid phase, and \(C_{\mathrm{EDL}}\) is the EDL
capacitance. Combining eq \ref{eqn-Delta-gamma-2DL-EDL-full} with eqs
\ref{eqn-def-Young-Delta-theta} and \ref{eqn-delta-gamma-sigma-free-2D},
the contact angle change due to the EDL effect, \((\Delta \cos
\theta)^{\mathrm{EDL}}\) is given by:
\begin{equation}
\label{eqn-Delta-cos-EDL}
(\Delta \cos \theta)^{\mathrm{EDL}} = -\frac{1}{\gamma_{\mathrm{L}}}
                                      \int_{0}^{\sigma_{\mathrm{L}}} \sigma' 
                                      \left(\frac{1}{C_{\mathrm{EDL}}}\right) \mathrm{d}\sigma'
\end{equation}
In other words, eqs \ref{eqn-delta-gamma-sigma-free-2D} and
\ref{eqn-Delta-gamma-2DL-EDL-full} suggest that \(\sigma_{\mathrm{2D}}\)
decreases both \(\gamma_{\mathrm{2D}}\) and \(\gamma_{\mathrm{2D-L}}\) to
the same extent, i.e. \(\int_{0}^{\sigma_{\mathrm{2D}}}
\sigma'/C_{\mathrm{2D}} \mathrm{d}\sigma'\), such that the contribution
of quantum capacitance cancels out in the YLE.
